%-------------------------
% Resume in Latex
% Author : Elliot Tuckerman
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabularx}{\textwidth}{Xr}
  \textbf{\Huge Elliot Tuckerman} & 
  \begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Address:} Norcross, GA, 30092, USA \\
    \textbf{Email:} \href{mailto:elliottuckerman99@gmail.com}{elliottuckerman99@gmail.com} \\
    \textbf{Mobile:} +1 (770) 871-6961 % updated to US format
  \end{minipage} \\
\end{tabularx}

% GitHub, LinkedIn, and Portfolio on the same line
\begin{tabular}{l l}
  \href{https://github.com/etuckerman}{GitHub} & \href{https://github.com/etuckerman}{https://github.com/etuckerman} \\
  \href{https://www.linkedin.com/in/elliottuckerman/}{LinkedIn} & \href{https://www.linkedin.com/in/elliottuckerman/}{https://www.linkedin.com/in/elliottuckerman/} \\
  \href{https://etuckerman.github.io}{Portfolio} & \href{https://etuckerman.github.io}{https://etuckerman.github.io}
\end{tabular}
\vspace{-0.1cm}
\begin{center}
  Green Card holder; relocated from the UK to the USA. \\
  Expertise in LLM optimization, NLP, and fine-tuning.
\end{center}
\vspace{-1cm}
%-----------SKILLS-----------------
\section{Skills}
 \resumeSubHeadingListStart
   \item \textbf{Languages:} Python, C++, C\#, SQL
   \item \textbf{Technologies:} NLP (spaCy, BERT, NLTK), Multi-GPU Training, Model Optimization
   \item \textbf{Tools:} TensorFlow, PyTorch, Hugging Face, Scikit-learn, XGBoost, AWS, Git, Jupyter
   \item \textbf{Practices:} Test-Driven Development (TDD), Object-Oriented Design (OOD), Version Control, Agile
 \resumeSubHeadingListEnd


\vspace{-0.5cm} % Adjust this value to reduce the gap

%-----------EDUCATION-----------------
\section{Education}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Sheffield Hallam University}{Sheffield, UK}
      {BSc in Computer Science; GPA: 4.0}{2020 -- 2024}
      \resumeItemListStart
        \resumeItem{Specialization}{Machine Learning and Heuristics}
        \resumeItem{Additional Coursework}{CS50's AI with Python (Harvard, edX), NLP with Transformers (Hugging Face)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-0.5cm} % Adjust this value to reduce the gap

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
  {META (via Apex Systems)}{Remote}
  {Gen AI Contractor, Security Delivery Management Team}{2025 – Present}
  \resumeItemListStart
    \resumeItem{Prompt Injection Mitigation}{Labeled and analyzed GenAI outputs to detect and prevent prompt injection attacks in UI-interacting agents.}
    \resumeItem{LLM Behavior Evaluation}{Tested agent behavior and safety within simulated user environments, contributing to alignment and robustness efforts.}
    \resumeItem{Synthetic Data Generation}{Intentionally triggered high-stakes agent actions and exported traces for manual annotation, producing high-quality training data for fine-tuning.}
    \resumeItem{MLE Collaboration}{Led meetings with Meta Machine Learning Engineers to propose improved methods for synthetic data generation and evaluation refinement.}
    \resumeItem{Secure AI Operations}{Collaborated with AI and security teams to support safe, high-quality deployment of foundation models.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-0.35cm}
\resumeSubHeadingListStart
\resumeSubheading
{SPRK}{Tampa, FL}
{Machine Learning Engineer, Syllabus AI }{2024 - Present}
\resumeItemListStart
\resumeItem{Data Parsing \& Extraction}{Built scalable parsing tools using LlamaParse to extract and process detailed imagery and table contents from syllabi and reading materials, reducing manual effort and improving accuracy.}
\resumeItem{Structured Data Pipeline}{Leveraged Qwen2.5-72B-Instruct to transform raw data into structured JSON, enabling applications like academic calendars and event notifications.}
\resumeItem{Multimodal RAG System}{Developed chatbot RAG systems for solving math problems and scheduling college events, integrating image parsing and agentic workflows for seamless user interaction.}
\resumeItem{State-of-the-Art Solutions}{Researched and implemented cutting-edge ML techniques, including advanced prompt engineering and model benchmarking, to ensure high performance and innovation.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-0.3cm}
\resumeSubHeadingListStart  
    \resumeSubheading
      {DataAnnotation.tech}{Atlanta, GA}
      {Machine Learning Engineer, LLM Optimization}{2023 - 2024}
      \resumeItemListStart
        \resumeItem{Code Evaluation}{Validated outputs from large language models.}
        \resumeItem{Optimization}{Enhanced code for improved performance.}
        \resumeItem{Model Management}{Supervised in-development model performance.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd
\vspace{-0.6cm}

\section{Projects}
    \resumeSubHeadingListStart  
      \resumeSubItem{Llama 3.1 QA Fine-tune}
        {Fine-tuned LLaMA 3.1 with TensorFlow, utilizing a custom dataset to improve language model performance for an RV company. Focused on optimization and evaluation.}
      \resumeSubItem{Multilingual Speech Application}
        {Commissioned by a customer service team to build a real-time multilingual speech application using MMS-TTS database. Implemented a queue system for translating and outputting multiple sentences simultaneously, producing live, natural-sounding voice translations.}
      \resumeSubItem{Multi-GPU LLM Fine Tuning}
        {Leveraged multi-GPU techniques in PyTorch to scale and optimize large language model training for improved efficiency.}
      \resumeSubItem{Vehicle Theft Analysis}
        {Implemented data analysis with Python and Scikit-learn to extract insights from stolen vehicle datasets and develop predictive models.}
    \resumeSubHeadingListEnd







\end{document}
