%-------------------------
% Resume in Latex
% Author : Elliot Tuckerman
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabularx}{\textwidth}{Xr}
  \textbf{\Huge Elliot Tuckerman} & 
  \begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Address:} Smyrna, GA, 30082, USA \\
    \textbf{Email:} \href{mailto:elliottuckerman99@gmail.com}{elliottuckerman99@gmail.com} \\
    \textbf{Mobile:} +1 (770) 871-6961 % updated to US format
  \end{minipage} \\
\end{tabularx}

% GitHub, LinkedIn, and Portfolio on the same line
\begin{tabular}{l l}
  \href{https://github.com/etuckerman}{GitHub} & \href{https://github.com/etuckerman}{https://github.com/etuckerman} \\
  \href{https://www.linkedin.com/in/elliottuckerman/}{LinkedIn} & \href{https://www.linkedin.com/in/elliottuckerman/}{https://www.linkedin.com/in/elliottuckerman/} \\
  \href{https://etuckerman.github.io}{Portfolio} & \href{https://etuckerman.github.io}{https://etuckerman.github.io}
\end{tabular}

\begin{center}
  Green Card holder; relocated from the UK to the USA. \\
  Expertise in LLM optimization, NLP, and fine-tuning.
\end{center}
\vspace{-1cm}
%-----------SKILLS-----------------
\section{Skills}
 \resumeSubHeadingListStart
   \item \textbf{Languages:} Python, C++, C\#, SQL
   \item \textbf{Technologies:} NLP (spaCy, BERT, NLTK), Multi-GPU Training, Model Optimization
   \item \textbf{Tools:} TensorFlow, PyTorch, Hugging Face, Scikit-learn, XGBoost, AWS, Git, Jupyter
   \item \textbf{Practices:} Test-Driven Development (TDD), Object-Oriented Design (OOD), Version Control, Agile
 \resumeSubHeadingListEnd


\vspace{-0.5cm} % Adjust this value to reduce the gap

%-----------EDUCATION-----------------
\section{Education}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Sheffield Hallam University}{Sheffield, UK}
      {BSc in Computer Science; GPA: 4.0}{2020 -- 2024}
      \resumeItemListStart
        \resumeItem{Specialization}{Machine Learning and Heuristics}
        \resumeItem{Relevant Coursework}{CS50's AI with Python (Harvard, edX), NLP with Transformers (Hugging Face)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-0.5cm} % Adjust this value to reduce the gap

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {SPRK}{Tampa, FL}
      {Machine Learning Engineer, Syllabus AI}{2024 - Present}
      \resumeItemListStart
        \resumeItem{Data Extraction}{Integrated LlamaParse to streamline the extraction of actionable data from college syllabi, greatly improving speed and accuracy. This cut manual processing time and ensured high-quality data.}
        \resumeItem{Data Structuring}{Employed Qwen2.5-72B-Instruct to interpret extracted data, organizing it into structured JSON format that includes event details like descriptions and due dates. This data structure facilitates applications like academic calendars and notifications.}
      \resumeItemListEnd
\



    \resumeSubheading
      {DataAnnotation.tech}{Atlanta, GA}
      {Machine Learning Engineer, LLM Optimization}{2023 - 2024}
      \resumeItemListStart
        \resumeItem{Code Evaluation}{Validated outputs from large language models.}
        \resumeItem{Optimization}{Enhanced code for improved performance.}
        \resumeItem{Model Management}{Supervised in-development model performance.}
      \resumeItemListEnd

    \resumeSubheading
      {Sheffield Hallam University}{Sheffield, UK}
      {Game Developer (C++)}{2020 -- 2024}
      \resumeItemListStart
        \resumeItem{AI Development}{Created AI for Tic-Tac-Toe and Minesweeper using advanced algorithms.}
        \resumeItem{Project Management}{Led team, managing tasks and timelines.}
        \resumeItem{Game Quality}{Produced high-performance, user-focused games.}
        \resumeItem{Awards}{Won "2D Game of the Year" for innovative design.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-0.5cm}


\section{Projects}
    \resumeSubHeadingListStart  
      \resumeSubItem{Llama 3.1 QA Fine-tune}
        {Fine-tuned LLaMA 3.1 with TensorFlow, utilizing a custom dataset to improve language model performance for an RV company. Focused on optimization and evaluation.}
      \resumeSubItem{Multilingual Speech Application}
        {Commissioned by a customer service team to build a real-time multilingual speech application using MMS-TTS database. Implemented a queue system for translating and outputting multiple sentences simultaneously, producing live, natural-sounding voice translations.}
      \resumeSubItem{Multi-GPU LLM Fine Tuning}
        {Leveraged multi-GPU techniques in PyTorch to scale and optimize large language model training for improved efficiency.}
      \resumeSubItem{AI-Powered CS:S Surfing Community Assistant}
        {Developed a Python-based AI assistant using NLP to enhance player interaction in Counter-Strike: Source’s surfing community.}
      \resumeSubItem{Vehicle Theft Analysis}
        {Implemented data analysis with Python and Scikit-learn to extract insights from stolen vehicle datasets and develop predictive models.}
      \resumeSubItem{PS5 3D Game Engine Development}
        {Engineered a high-performance PS5 game engine using the Sony PS5 SDK, optimizing graphics and performance.}
      \resumeSubItem{Unity Advanced Movement System}
        {Developed an advanced movement system in Unity, enhancing physics realism and gameplay mechanics.}
      \resumeSubItem{Personal Portfolio Website}
        {Designed and developed a responsive portfolio website using HTML, CSS, and JavaScript. Hosted on GitHub Pages with a focus on showcasing AI/ML projects, blog posts, and technical skills.}
    \resumeSubHeadingListEnd






\end{document}
