%-------------------------
% Resume in Latex
% Author : Elliot Tuckerman
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabularx}{\textwidth}{Xr}
  \textbf{\Huge Elliot Tuckerman} & 
  \begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Address:} Sheffield, UK \\
    \textbf{Email:} \href{mailto:elliottuckerman99@gmail.com}{elliottuckerman99@gmail.com} \\
    \textbf{Mobile:} +44 7908 756278
  \end{minipage} \\
\end{tabularx}

\begin{tabular}{l l}
  \href{https://github.com/etuckerman}{GitHub} & \href{https://github.com/etuckerman}{https://github.com/etuckerman} \\
  \href{https://www.linkedin.com/in/elliottuckerman/}{LinkedIn} & \href{https://www.linkedin.com/in/elliottuckerman/}{https://www.linkedin.com/in/elliottuckerman/} \\
  \href{https://etuckerman.github.io}{Portfolio} & \href{https://etuckerman.github.io}{https://etuckerman.github.io}
\end{tabular}

\vspace{-0.2cm}
\begin{center}
FAANG-experienced AI \& Software Engineer specialising in LLM security and scalable systems.
\end{center}
\vspace{-0.8cm}

%-----------SKILLS-----------------
\section{Skills}
 \resumeSubHeadingListStart
   \item \textbf{Languages:} Python, C++, C\#, SQL
   \item \textbf{Technologies:} NLP (spaCy, BERT, NLTK), Multi-GPU Training, Model Optimization
   \item \textbf{Tools:} TensorFlow, PyTorch, Hugging Face, Scikit-learn, XGBoost, AWS, Git, Jupyter
   \item \textbf{Practices:} TDD, OOD, Version Control, Agile
 \resumeSubHeadingListEnd

\vspace{-0.5cm}

%-----------EDUCATION-----------------
\section{Education}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Sheffield Hallam University}{Sheffield, UK}
      {BSc in Computer Science; GPA: 4.0}{2020 -- 2024}
      \resumeItemListStart
        \resumeItem{Specialization}{Machine Learning and Heuristics}
        \resumeItem{Additional Coursework}{CS50's AI with Python (Harvard, edX), NLP with Transformers (Hugging Face)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-0.5cm}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
  {META}{Atlanta, GA, USA}
  {Gen AI Contractor, Security Delivery Management Team}{2025 – 2026}
  \resumeItemListStart
    \resumeItem{Prompt Injection Mitigation}{Labeled and analyzed GenAI outputs to detect and prevent prompt injection attacks in UI-interacting agents.}
    \resumeItem{LLM Behavior Evaluation}{Tested agent behavior and safety within simulated environments, contributing to alignment and robustness efforts.}
    \resumeItem{Synthetic Data Generation}{Triggered high-stakes agent actions and exported traces for manual annotation, producing high-quality fine-tuning data.}
    \resumeItem{MLE Collaboration}{Led discussions with ML engineers to improve synthetic data generation and evaluation refinement.}
    \resumeItem{Secure AI Operations}{Collaborated with AI and security teams to support safe deployment of foundation models.}
  \resumeItemListEnd

  \resumeSubheading
  {SPRK}{Tampa, FL, USA}
  {Machine Learning Engineer, Prompt Engineer}{2024 – 2025}
  \resumeItemListStart
    \resumeItem{Data Parsing \& Extraction}{Built scalable parsing tools using LlamaParse to extract imagery and tabular content from academic documents.}
    \resumeItem{Structured Data Pipeline}{Used Qwen2.5-72B-Instruct to transform raw data into structured JSON for academic applications.}
    \resumeItem{Multimodal RAG System}{Developed math-solving and scheduling chatbot systems integrating image parsing and agent workflows.}
    \resumeItem{Advanced Prompt Engineering}{Researched and benchmarked state-of-the-art models to optimize performance.}
  \resumeItemListEnd

  \resumeSubheading
  {DataAnnotation.tech}{Atlanta, GA, USA}
  {Machine Learning Engineer, LLM Optimization}{2023 – 2024}
  \resumeItemListStart
    \resumeItem{Code Evaluation}{Validated outputs from large language models.}
    \resumeItem{Optimization}{Enhanced generated code for performance and correctness.}
    \resumeItem{Model Supervision}{Monitored and guided in-development model performance.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-0.75cm}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart  
  \resumeSubItem{Llama 3.1 QA Fine-tune}
    {Fine-tuned LLaMA 3.1 with TensorFlow using a custom dataset to improve domain-specific QA performance.}
  \resumeSubItem{Multilingual Speech Application}
    {Built a real-time multilingual speech system using MMS-TTS with queue-based translation and live audio output.}
  \resumeSubItem{Multi-GPU LLM Fine-Tuning}
    {Implemented distributed training in PyTorch to scale large language model optimization.}
  \resumeSubItem{Vehicle Theft Analysis}
    {Developed predictive models using Python and Scikit-learn to extract insights from crime datasets.}
\resumeSubHeadingListEnd

\end{document}